\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-10-02 paper2015asml.tex
typo
modified the spacing of some figs and tables, removed some lines
spacing and formatting changes

\begin{table*}[t]
\centering
\scalebox{0.9}{
\begin{tabular}{|c||c|c|c|c|c|c|c|}
\hline
Efficiency  & Highly inefficient& Moderately inefficient& Slightly inefficient& Neutral & Slightly efficient& Moderately efficient& Highly efficient\\
\hline
Elegance    & Highly awkward& Moderately awkward& Slightly awkward& Neutral & Slightly elegant& Moderately elegant& Highly elegant\\
\hline
Smoothness  & Highly rough& Moderately rough& Slightly rough& Neutral & Slightly smooth& Moderately smooth& Highly smooth\\
\hline
Overall     & Extremely poor& Moderately poor& Somewhat poor& Neutral & Somewhat good& Moderately good& Extremely good\\
\hline
\end{tabular}
}
\caption{The four rating categories/attributes and the associated scales for each presented to the survey respondent.}
\label{tab:rating_scales}
\end{table*}

@@

\section{Survey Results and Analysis}
\label{sec:raw_results}
The survey resulted in at least 20 ratings for each trajectory (so there were a total of 2060 ratings from participants in the survey). In this section, we will first analyze the raw results from the survey (which are interesting in themselves). Subsequently, we will present a set of features that were used to represent individual trajectories. These features will be used in the next section to learn the human-observer ratings for robot trajectories. 
\subsection{Raw Survey Results}
\begin{figure}[h]
  \centering{\includegraphics[width=0.45\linewidth]{pictures/efficiency}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/elegant}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/smooth}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/overall}}
  \caption{Histogram of averaged ratings for the 4 different attributes for 103 trajectories. Clockwise from top left: Efficient vs. Inefficient, Elegant vs. Awkward, Smooth vs. Rough, Overall Rating}
\label{fig:survey_raw}
\end{figure}
The raw results of the survey are summarized in Fig.~\ref{fig:survey_raw} which shows a histogram of averaged responses for each of the four survey questions across the 103 trajectories that were rated by users. It is clear that a majority of the trajectories in our survey were well received by the human observers but there were quite a few trajectories that were rated badly as well. An analysis of the ratings for each trajectory showed that four (averaged) ratings for each individual trajectory were always similar to each other, indicating that users had similar preferences for each trajectory regardless of the individual attributes used to describe the preference for the trajectory (efficient, elegant, smooth, overall). Table~\ref{tab:correlation} shows the Pearson's correlation coefficients corresponding to pairs of attributes. Attributes across individual questions are highly correlated at a statistically significant level of 1\% (with p-values $< 0.01\%$). The 95\% confidence intervals for all the four ratings for each trajectory was less than 1.0. 
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
& Efficient & Elegant & Smooth & Overall \\ \hline
Efficient & 1 & 0.96 & 0.91 & 0.98 \\ \hline
Elegant & 0.96 & 1 & 0.96 & 0.98 \\ \hline
Smooth & 0.91 & 0.96 & 1 & 0.96 \\ \hline
Overall & 0.98 & 0.98 & 0.96 & 1 \\ \hline
\end{tabular}
\caption{Correlation between the four attributes in the survey.}
\label{tab:correlation}
\end{table}

@@

{\bf Hausdorff Distance:}
The Hausdorff distance $H_\text{AB}$ between trajectory $\xi_\text{A}$ and trajectory $\xi_\text{B}$ can be computed as follows:
\begin{equation}
\begin{aligned}
H_\text{AB} &= \max (h_{\text{AB}}, h_{\text{BA}}) \\
h_{\text{AB}} &= \max_{q_\text{A} \in \xi_\text{A}} \min_{q_\text{B} \in \xi_\text{B}} \text{d}(q_\text{A}, q_\text{B})\\
h_{\text{BA}} &= \max_{q_\text{B} \in \xi_\text{B}} \min_{q_\text{A} \in \xi_\text{A}} \text{d}(q_\text{B}, q_\text{A})\\
\end{aligned}
\end{equation}

@@

\begin{table}
\label{tab:feature_description}
\scalebox{0.9}{
\centering
\begin{tabular}{|p{0.3\columnwidth}|p{0.2\columnwidth}|p{0.5\columnwidth}|}
\hline
Feature Name & Metric & Feature Description \\
\hline
path\_length, smoothness, clearance, max\_lin\_acc, joint\_limit\_distance & Joint-space & Features discussed in Section~\ref{subsec:traj_feat} computed on joint-space trajectory \tj{}\\
\hline
[link]\_length, [link]\_smoothness, [link]\_max\_curvature, [link]\_lin\_acc, [link]\_quat\_dist & Cartesian & Features discussed in Section~\ref{subsec:traj_feat} computed on 3D cartesian path traced by [link] in \tj{}\\
\hline
h\_[link]\_bfs, h\_[link1]\_[link2], H\_[link]\_bfs, H\_[link1]\_[link2] & Cartesian & Assymetric ($h$) or symmetric ($H$) hausdorff distance between 3D path of [link] w.r.t BFS path or between 3D paths of [link1] and [link2]\\
\hline
[link]\_bfs\_dtw, [link1]\_[link2]\_dtw & Cartesian & DTW cost between path of [link] and the BFS path, or between paths of [link1] and [link2]\\
\hline
\end{tabular}
}
\caption{The complete list of computed trajectory features used for classification.}
\end{table}

\begin{figure}[h]
\centering
\begin{tabular}{|c|cc|}%p{0.4\columnwidth}p{0.4\columnwidth}}
\hline
& Low feature-value & High feature-value \\
\hline
\rot{wrist\_tool\_dtw} & 
\adjincludegraphics[trim={.1\width} {.080\height} {.25\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{low}{0}} & 
\adjincludegraphics[trim={.2\width} {.0\height} {.2\width} {.15\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{high}{0}} \\

@@

\rot{wrist\_bfs\_dtw} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{low}{0}} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{high}{0}} \\
\hline
\end{tabular}
\caption{Example trajectories for different values of the most useful features. Trajectories on the left have low feature values while trajectories on the right have high features values for each corresponding feature in that row.}\label{fig:example_features}
\end{figure}

@@

\section{Conclusion}
\label{sec:conclusion}
In this work, we have gathered ratings for a large dataset of robot trajectories. We have already gained significant insights into the 
types of trajectories that are preferred by human observers. In particular, we have been able to identify a set of features that seem to influence 
the human's perception of the trajectories the most. This can help us in defining better cost functions when generating the trajectories. The classifiers 
that we have learned could also be used to directly inform gradient free motion planning algorithms by assigning a rating to new trajectories. Our 
results were generated using a single robot model (the PR2) but we believe that they will easily translation to other robot models as well. To this end, 
we will keep the survey open and attempt to collect data for a larger set of trajectories in 
more environments and with different robots.

>>>>

\begin{table*}[t]
\centering
\scalebox{0.9}{
\begin{tabular}{cccccccc}
&&&&&&&\\
\hline
Efficiency  & Highly inefficient& Moderately inefficient& Slightly inefficient& Neutral & Slightly efficient& Moderately efficient& Highly efficient\\
\hline
Elegance    & Highly awkward& Moderately awkward& Slightly awkward& Neutral & Slightly elegant& Moderately elegant& Highly elegant\\
\hline
Smoothness  & Highly rough& Moderately rough& Slightly rough& Neutral & Slightly smooth& Moderately smooth& Highly smooth\\
\hline
Overall     & Extremely poor& Moderately poor& Somewhat poor& Neutral & Somewhat good& Moderately good& Extremely good\\
\hline
\end{tabular}
}
\caption{The four rating categories/attributes and the associated scales for each presented to the survey respondent.}
\label{tab:rating_scales}
\end{table*}

@@

\section{Survey Results and Analysis}
\label{sec:raw_results}
The survey resulted in at least 20 ratings for each trajectory (so there were a total of 2060 ratings from participants in the survey). In this section, we will first analyze the raw results from the survey (which are interesting in themselves). Subsequently, we will present a set of features that were used to represent individual trajectories. These features will be used in the next section to learn the human-observer ratings for robot trajectories. 
\subsection{Raw Survey Results}
\begin{figure}[h]
  \centering{\includegraphics[width=0.45\linewidth]{pictures/efficiency}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/elegant}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/smooth}}
  \centering{\includegraphics[width=0.45\linewidth]{pictures/overall}}
  \caption{Histogram of averaged ratings for the 4 different attributes for 103 trajectories. Clockwise from top left: Efficient vs. Inefficient, Elegant vs. Awkward, Smooth vs. Rough, Overall Rating}
\label{fig:survey_raw}
\end{figure}
The raw results of the survey are summarized in Fig.~\ref{fig:survey_raw} which shows a histogram of averaged responses for each of the four survey questions across the 103 trajectories that were rated by users. It is clear that a majority of the trajectories in our survey were well received by the human observers but there were quite a few trajectories that were rated badly as well. An analysis of the ratings for each trajectory showed that four (averaged) ratings for each individual trajectory were always similar to each other, indicating that users had similar preferences for each trajectory regardless of the individual attributes used to describe the preference for the trajectory (efficient, elegant, smooth, overall). Table~\ref{tab:correlation} shows the Pearson's correlation coefficients corresponding to pairs of attributes. Attributes across individual questions are highly correlated at a statistically significant level of 1\% (with p-values $< 0.01\%$). The 95\% confidence intervals for all the four ratings for each trajectory was less than 1.0. 
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline
& Efficient & Elegant & Smooth & Overall \\ \hline
Efficient & 1 & 0.96 & 0.91 & 0.98 \\ \hline
Elegant & 0.96 & 1 & 0.96 & 0.98 \\ \hline
Smooth & 0.91 & 0.96 & 1 & 0.96 \\ \hline
Overall & 0.98 & 0.98 & 0.96 & 1 \\ \hline
\end{tabular}
\caption{Correlation between the four attributes in the survey.}
\label{tab:correlation}
\vspace{-0.1in}
\end{table}

@@

{\bf Hausdorff Distance:}
The Hausdorff distance $H_\text{AB}$ between trajectory $\xi_\text{A}$ and $\xi_\text{B}$ can be computed as follows:
\begin{equation}
\begin{aligned}
H_\text{AB} &= \max (h_{\text{AB}}, h_{\text{BA}}) \\
h_{\text{AB}} &= \max_{q_\text{A} \in \xi_\text{A}} \min_{q_\text{B} \in \xi_\text{B}} \text{d}(q_\text{A}, q_\text{B})\\
h_{\text{BA}} &= \max_{q_\text{B} \in \xi_\text{B}} \min_{q_\text{A} \in \xi_\text{A}} \text{d}(q_\text{B}, q_\text{A})\\
\end{aligned}
\end{equation}

@@

\begin{table}
\label{tab:feature_description}
\scalebox{0.9}{
\centering
\begin{tabular}{p{0.3\columnwidth}p{0.2\columnwidth}p{0.5\columnwidth}}
&&\\
\hline
Feature Name & Metric & Feature Description \\
\hline
path\_length, smoothness, clearance, max\_lin\_acc, joint\_limit\_distance & Joint-space & Features discussed in Section~\ref{subsec:traj_feat} computed on joint-space trajectory \tj{}\\
\hline
[link]\_length, [link]\_smoothness, [link]\_max\_curvature, [link]\_lin\_acc, [link]\_quat\_dist & Cartesian & Features discussed in Section~\ref{subsec:traj_feat} computed on 3D cartesian path traced by [link] in \tj{}\\
\hline
h\_[link]\_bfs, h\_[link1]\_[link2], H\_[link]\_bfs, H\_[link1]\_[link2] & Cartesian & Assymetric ($h$) or symmetric ($H$) hausdorff distance between 3D path of [link] w.r.t BFS path or between 3D paths of [link1] and [link2]\\
\hline
[link]\_bfs\_dtw, [link1]\_[link2]\_dtw & Cartesian & DTW cost between path of [link] and the BFS path, or between paths of [link1] and [link2]\\
\hline
\end{tabular}
}
\caption{The complete list of computed trajectory features used for classification.}
\vspace{-0.2in} 
\end{table}

\begin{figure}[h]
\centering
\begin{tabular}{ccc}%p{0.4\columnwidth}p{0.4\columnwidth}}
&&\\
\hline
& Low feature-value & High feature-value \\
\hline
\rot{wrist\_tool\_dtw} & 
\adjincludegraphics[trim={.1\width} {.080\height} {.25\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{low}{0}} & 
\adjincludegraphics[trim={.2\width} {.0\height} {.2\width} {.15\height}, clip, width=0.4\columnwidth]{\fta{wrist_tool_dtw}{high}{0}} \\

@@

\rot{wrist\_bfs\_dtw} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{low}{0}} & 
\adjincludegraphics[trim={.1\width} {.0\height} {.1\width} {.0\height}, clip, width=0.4\columnwidth]{\fta{wrist_bfs_dtw}{high}{0}} \\
\hline
\end{tabular}
\caption{Example trajectories for different values of the most useful features. Trajectories on the left have low feature values while trajectories on the right have high features values for each corresponding feature in that row.}\label{fig:example_features}
\vspace{-0.2in} 
\end{figure}

@@

\section{Conclusion}
\label{sec:conclusion}
In this work, we have gathered ratings for a large dataset of robot trajectories. We have already gained significant insights into the 
types of trajectories that are preferred by human observers. In particular, we have been able to identify a set of features that seem to influence 
the human's perception of the trajectories the most. This can help us in defining better cost functions when generating the trajectories. The classifiers 
that we have learned could also be used to directly inform gradient free motion planning algorithms by assigning a rating to new trajectories. Our 
results were generated using a single robot model (the PR2) but we believe that they will easily translate to other robot models as well. To this end, 
we will keep the survey open and attempt to collect data for a larger set of trajectories in 
more environments and with different robots.
